---
surname: Francesco Beghini, PhD
# profilepic: fbeghini.jpg
position: "Postdoctoral Associate"
address: "17 Hillhouse Ave., New Haven, CT, 06511"
phone: (203) 627 4220
email: "francesco.beghini@yale.edu"
twitter: chocophlan
github: fbeghini
orcid: '0000-0002-8105-9607'
headcolor: "333333"
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(rorcid)
library(dplyr)
library(tibble)
myorcid <- '0000-0002-8105-9607'
Sys.setenv(ORCID_TOKEN = '5f86130a-e14f-42f8-92bb-afffa303fcde')
#x <- orcid_auth()
#orcid_auth(reauth = TRUE)
```


# Education

```{r}
do.call('bind_rows', orcid_educations(myorcid)[[myorcid]]$`affiliation-group`$summaries) %>% 
  transmute(Institution = `education-summary.organization.name`,
            Degree = `education-summary.role-title`,
            Year = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}", .na = 'current'),
            Where = stringr::str_c(`education-summary.organization.address.city`, `education-summary.organization.address.country`, sep = ', ')) %>% 
  detailed_entries(Institution, Year, Degree, Where)
```


# Positions

```{r}
tribble(~Date, ~What, ~Descr, ~With,
        '04/2022 - Current', 'Postdoctoral Associate at Human Nature Lab, Yale University', '', 'Mentor: Prof. Nicholas Christakis',
        '09/2021 - 04/2022', 'Postdoctoral Fellow at Segata Lab, UniTN', '', 'Mentor: Prof. Nicola Segata',
        '05/2021 - 08/2021', 'Consultant for Human Nature Lab, Yale University', '','Mentor: Prof. Nicholas Christakis',
        '11/2015 - 11/2017', 'Internship at Segata Lab, UniTN', '', 'Mentor: Prof. Nicola Segata',
        '02/2017 - 03/2017', 'Internship at School of Public Health, CUNY', '', 'Mentor: Prof. Levi Waldron',
        '11/2014 - 09/2015', 'Internship at Segata Lab, UniTN', '', 'Mentor: Prof. Nicola Segata',
) %>% 
  detailed_entries(what = Descr, when = Date, with = What, where = With)
```



\newpage

# Publications

```{r}
rorcid::orcid_works(myorcid)[[myorcid]]$works %>% 
  rowwise %>% 
  mutate( contributor = stringr::str_c(orcid_works(myorcid, put_code = `put-code`)[[myorcid]]$works$contributor[[1]][[1]][,1], collapse =', ')) %>% 
  ungroup() %>% 
  transmute ( bibtype = "Article",
              title = `title.title.value`,
              author = contributor,
              journaltitle = stringr::str_replace(`journal-title.value`, '&', ' and '),
              year = stringr::str_c(`publication-date.year.value`, `publication-date.month.value`, sep = '-'),
              key = row_number()
            ) %>% 
  arrange(desc(year)) %>%
  # RefManageR::as.BibEntry() %>%
  # RefManageR::WriteBib("fbeghini.bib")
  # bibliography_entries("fbeghini.bib")
  vitae::detailed_entries(what = author, when = year, where = journaltitle, with = title)
```


<!-- # Submitted papers -->
<!-- ```{r} -->
<!-- tribble(~Authors, ~Title, ~Journal,  -->
<!--         'Michele Tomasi, Francesco Beghini, Ilaria Zanella, Laura Fantappie, Carmela Irene, Luca Frattini, Giulia Masetti, Samine Jessica Isaac, Enrico König, Federica Armanini, Alberto Grandi, Nicola Segata, Guido Grandi', 'Commensal Bifidobacterium strains enhance the efficacy of neo-epitope based cancer vaccines', 'Frontiers in Oncology' -->
<!-- ) %>%  -->
<!--   detailed_entries(what = Authors, where = Journal, with = Title) -->
<!-- ``` -->

# Teaching
```{r}
tribble(~Date, ~What, ~Descr, ~With,
'10/2015 - 06/2018', 'Tutor at CIBIO - University of Trento', '"Computer Science" and "Computational Biology" tutor for CIBIO Undergraduate students', 'Prof. Andrea Passerini'
) %>% 
  detailed_entries(what = Descr, when = Date, with = What, where = With)
```

# Courses
```{r}
tribble(
  ~day, ~Title, ~Location,
  '25/9/2019', 'EMBO Practical Course - Bioinformatics and genome analyses. Teaching assistant for the "Shotgun metagenomics" session', 'San Michele all\'Adige, Italy'
) %>% 
  detailed_entries(what = Title, when = day, with = Location)
```

# Talks

```{r}
tribble(
  ~day, ~Title, ~Location,
  '21/11/2021', 'Integrating taxonomic, functional, and strain-level profiling of diverse microbial communities with bioBakery 3', 'Microbiome Virtual International Forum',
  '01/10/2020', 'Shotgun metagenomics for species and strain-level analysis', 'Yale University - New Haven',
  '08/10/2019', 'Large-scale microbial genomics for strain-level metagenomic analysis','University of Trento - Italy',
  '02/03/2017', 'Brief lesson given to Epidemiology PhD students about metagenomics, oral microbiome and the NYC-HANES II project', 'City University of New York - New York',
  '23/02/2017', 'Smoking and the oral microbiome in the New York City Health and Nutrition Examination Study (NYC-HANES II)', 'Columbia University - New York',
  '22/02/2017', 'Smoking and the oral microbiome in the New York City Health and Nutrition Examination Study (NYC-HANES II)', 'City University of New York - New York',
  '14/02/2017', 'Smoking and the oral microbiome in the New York City Health and Nutrition Examination Study (NYC-HANES II)', 'Albert Einstein Medical College of Medicine - New York',
  '13/02/2017', 'Smoking and the oral microbiome in the New York City Health and Nutrition Examination Study (NYC-HANES II)', 'New York University - New York'
) %>% 
  detailed_entries(what = Title, when = day, with = Location)
```

# Awards

```{r}
tribble(~Date, ~Title, ~Description,
        '08/2019', 'Prêmio Octavio Frias de Oliveira','Co-recipient of the award for the paper "Metagenomic analysis of colorectal cancer datasets identifies cross-cohort microbial diagnostic signatures and a link with choline degradation"',
        '02/2017', 'Microbiome in Health and Disease – Keystone Symposia, Colorado, USA', 'I was awarded 1,200$ as recipient of the Keystone Symposia “Future of Science” scholarship and selected for a poster entitled “Large-scale metagenomic analysis of Blastocystis in the human gut revealed high prevalence and association with BMI and archaeal abundance”'
) %>% 
  detailed_entries(when = Date, with = Title, what = Description)
```

# Student co-supervision
```{r}
tribble(~Date, ~What, ~Descr, ~With,
'2021-', 'Shivkumar Vishnempet Shridhar (PhD Biomedical Engineering - Yale University', '', 'Supervisor: Prof. Nicholas Christakis',
'2021-2023', 'Jackson Pullman (BSc Data Science - Yale University)', '','Supervisor: Prof. Nicholas Christakis',
'2019', 'Eleonora Nigro (MSc Quantitative and Computational Biology - CIBIO)', 'Expanding the genetic diversity of the Elusimicrobia bacterial phylum by multi-environment metagenomic analysis', 'Supervisor: Prof. Nicola Segata'
) %>% 
  detailed_entries(what = Descr, when = Date, with = What, where = With)
```

# Posters
```{r}
tribble(~Date, ~Location, ~Authors, ~Title,
'06/2018', 'BITS - Turin, Italy', 'Asnicar Francesco, Beghini Francesco, Bolzan Mattia, Manara Serena, Pasolli Edoardo, Mirarab Siavash, Huttenhower Curtis, Segata Nicola','An integrated pipeline for large-scale phylogenetic characterization of genomes and metagenomes',
'06/2018', 'Leading Edge Conference on Water and Wastewater Technologies - Edinburgh, UK', 'Petrini Serena, Foladori Paola, Beghini Francesco, Armanini Federica, Segata Nicola, Andreottola Gianni', 'Nutrient removal and microbial community analysis of a stable microalgal-bacterial consortium treating real municipal wastewater',
'02/2017', 'Microbiome in Health and Disease – Keystone Symposia, Colorado, USA', 'Francesco Beghini, Edoardo Pasolli, Duy Tin Truong, Lorenza Putignani, Simone M. Cacciò, Nicola Segata', 'Large-scale metagenomic analysis of Blastocystis in the human gut revealed association with Body Mass Index and archaeal abundance',
'04/2017', 'ECCMID – Wien, Austria', 'Serena Manara, Edoardo Pasolli, Daniela Dolce, Federica Armanini, Francesco Beghini, Novella Ravenni, Erica Camera, Grazia Dinnella, Paola Gualdi, Michele Schinella, Silvia Campana, Ermanno Baldo, Giovanni Taccetti, Nicola Segata', 'Genomic and metagenomic-based epidemiology and transmission networks of MRSA in two Italian hospitals',
'07/2017', 'CAMDA2017 – Prague, Czech Republic', 'Moreno Zolfo, Federica Pinto, Francesco Asnicar, Francesco Beghini, Paolo Manghi, Edoardo Pasolli, Adrian Tett and Nicola Segata', 'Strain-level bacterial and viral diversity in the MetaSUB dataset'
) %>%
  detailed_entries(when = Date, with = Title, what = Authors, where = Location)

```

# Languages
Italian: Mother tongue

Spanish: Bilingual proficiency

English: Professional working proficiency


# Skills
I have a very good experience with Linux, MacOS, and Windows OS’ with a good knowledge of bioinformatic and several computational biology tools. 

I use Bash, R and Python every day. Other known programming languages are Java, C/C++/C#, JavaScript, PHP, SQL and the .NET framework. 

During the laboratory trainee activities in my BSc and MSc I acquired some molecular biology related skills and during my internship at the Waldron Lab I acquired statistical and basic epidemiology skills.
